---
title: "UCI HAR Dataset Project Code Book"
output: 
    html_document:
        keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

This project reads in files from the UCI HAR Dataset and creates two tidy
datasets as R data.frame objects.

The project uses the dplyr and readr packages.

```{r echo=TRUE, warning=FALSE, message=FALSE}
source("run_analysis.R")
```

## Dataset: combined_data

The first dataset, combined_data, joins the information from the
following files:

* UCI HAR Dataset/activity_labels.txt: maps activity ID to activity name
* UCI HAR Dataset/features.txt: maps column index to variable name (561 variables)
* UCI HAR Dataset/train/X_train.txt: numeric train data, 561 columns, 1 for each variable
* UCI HAR Dataset/train/Y_train.txt: integer activity ID for each row of train data
* UCI HAR Dataset/train/subject_train.txt: integer subject ID for each row of train data
* UCI HAR Dataset/test/X_test.txt: numeric test data, 561 columns, 1 for each variable
* UCI HAR Dataset/test/Y_test.txt: integer activity ID for each row of test data
* UCI HAR Dataset/test/subject_test.txt: integer subject ID for each row of test data

A subset of 66 variables computing the mean and standard deviation of each 
measurement was selected from the original list of 561 variables. For more 
detailed information about the original dataset, see UCI HAR Dataset/README.txt 
and UCI HAR Dataset/features_info.txt.

The activity ID was converted from an integer to a text descriptor (factor 
variable).  A test/train subset identifier (factor variable) was created to
identify the subset in the combined dataset.

The combined_data dataset joins the subset ID, subject ID, and activity ID 
columns to the data variables and combines the test and train data in a single table.

```{r, combined_data_info}
str(combined_data)
```

## Dataset: summarized_data

The second dataset, summarized_data, computes the mean value of the 66 variables
for each subject and activity.

```{r, summarized_data_info}
str(summarized_data)
```
